---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# searchNHP

Non-human primate search filter terms

<!-- badges: start -->
<!-- badges: end -->

The goal of searchNHP is to is to provide users with an easy way to obtain a comprehensive list of search filters to use in popular databases such as PubMed, PsicInfo and Web of Science.

## Installation

You can install the released version of searchNHP from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("searchNHP")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("avrincon/searchNHP")
```
## Example

```{r example}
library(searchNHP)
## basic example code
```

The core function of this package is search_nhp().

The function arguments are:


By default the function returns search terms for all non-human primates.

```{r}
# by default function returns search terms for all NHPs
search_nhp(database = "PubMed")
```

Or you can explicitly specify all NHPs (gives same result as above)

```{r}
search_nhp(database = "PubMed", taxa = "NHPs")
```

You can specify single taxa or several

```{r}
search_nhp(database = "PsycInfo", taxa = "macaca")
search_nhp(database = "WebOfScience", taxa = c("papio", "theropithecus", "mandrillus"))
```

You can also exclude a taxonomic group(s) that occurs within "taxa"

```{r}
search_nhp(database = "WebOfScience", taxa = "hominidae", exclude = "pongo")
```

