---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# filterNHP

Non-human primate search filters

<!-- badges: start -->
<!-- badges: end -->

The goal of filterNHP is to is to provide users with an easy way to obtain a comprehensive search filters to use in popular databases such as 
[PubMed](https://pubmed.ncbi.nlm.nih.gov/), 
[PsycInfo](http://search.ebscohost.com/Login.aspx?profile=web&defaultdb=psyh&lp=login.asp&ref=https%3A%2F%2Fwww%2Egoogle%2Ecom%2F&authtype=ip,uid) 
and 
[Web of Science](http://login.webofknowledge.com/error/Error?Error=IPError&PathInfo=%2F&RouterURL=http%3A%2F%2Fwww.webofknowledge.com%2F&Domain=.webofknowledge.com&Src=IP&Alias=WOK5).

## Installation

You can install the released version of filterNHP from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("filterNHP")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("avrincon/filterNHP")
```
## Example

```{r example}
library(filterNHP)
## basic example code
```

The core function of this package is filter_nhp().

The function arguments are:


By default the function returns search terms for all non-human primates.

```{r}
# by default function returns search terms for all NHPs
filter_nhp(database = "PubMed")
```

Or you can explicitly specify all NHPs (gives same result as above)

```{r}
filter_nhp(database = "PubMed", taxa = "nonhuman_primates")
```

You can specify single taxa or several

```{r}
filter_nhp(database = "PsycInfo", taxa = "macaca")
filter_nhp(database = "WebOfScience", taxa = c("papio", "theropithecus", "mandrillus"))
```

You can also exclude a taxonomic group(s) that occurs within "taxa"

```{r}
filter_nhp(database = "WebOfScience", taxa = "hominidae", exclude = "pongo")
```

